\textbf{ Joystream: A Protocol for User Governed Content Platforms }

### 2019-02-25 paper.tex
Fix grammar

Some of the assets that are of value to the platform will inevitably not live in the state of the same blockchain. This could for example be state of a DNS mapping which lives on some other system, like ENS \cite{ens} or Handshake \cite{handshake}. It may even be desirable to move certain  assets from the Joystream blockchain, such as tokens, over onto other blockchain systems. While proposals are being developed to support very general inter blockchain transaction routine, such as Cosmos \cite{cosmos} for tokens and Polkadot \cite{polkadot}, its not clear when or if they will be fully deployed, and to what extent the Joystream blockchain will be able to benefit, or more simply whether the Joystream governance process will converge on such an integration.

>>>>

Some of the assets that are of value to the platform will inevitably not live in the state of the same blockchain. This could for example be state of a DNS mapping which lives on some other system, like ENS \cite{ens} or Handshake \cite{handshake}. It may even be desirable to move certain  assets from the Joystream blockchain, such as tokens, over onto other blockchain systems. While proposals are being developed to support very general inter blockchain transaction routinely, such as Cosmos \cite{cosmos} for tokens and Polkadot \cite{polkadot}, its not clear when or if they will be fully deployed, and to what extent the Joystream blockchain will be able to benefit, or more simply whether the Joystream governance process will converge on such an integration.
